---
title: "RNAseq viewer report"
author: "`r params$author`"
output: 
    flexdashboard::flex_dashboard:
        vertical_layout: scroll
        orientation: rows
params:
  nr: NA
  bpnr: NA
  ccnr: NA
  mfnr: NA
  nrdown: NA
  bpnrdown: NA
  mfnrdown: NA
  ccnrdown: NA
  variablepca: NA
  tempdir: NA
  gseanr: NA
  author: NA
---

```{r results="asis", echo=FALSE}
cat("
<style>
.navbar-inverse .navbar-nav>li>a {
    color: #ffffff;
    background-color: #334969;
}

.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
    color: #ffffff;
    background-color: #3b5e86;
}

.navbar-inverse .navbar-collapse, .navbar-inverse .navbar-form {
    border-color: #396596;
    background-color: #334969;
}

.container-fluid {
    background-color: #334969;
}

.navbar-inverse .navbar-nav > .open > a, .navbar-inverse .navbar-nav > .open > a:hover, .navbar-inverse .navbar-nav > .open > a:focus {
    background-color: #3b5e86;
    color: #ffffff;

}

.dropdown-menu > .active > a, .dropdown-menu > .active > a:hover, .dropdown-menu > .active > a:focus {
    color: #ffffff;
    text-decoration: none;
    outline: 0;
    background-color: #3b5e86;
}

.navbar-inverse .navbar-nav > li > a:hover, .navbar-inverse .navbar-nav > li > a:focus {

    color: #ffffff;
    background-color: #3b5e86;
}

.navbar-inverse .navbar-nav > .open > a, .navbar-inverse .navbar-nav > .open > a:hover, .navbar-inverse .navbar-nav > .open > a:focus {

    background-color: #3b5e86;
    color: #ffffff;
}
.dropdown-menu > li > a:hover, .dropdown-menu > li > a:focus {
    text-decoration: none;
    color: #ffffff;
    background-color: #3b5e86;
}
</style>
")
```

```{r setup, echo=FALSE, include=FALSE, comment=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.width = 12, eval=FALSE)

library('dygraphs')
library('flexdashboard')
library('shinydashboard')
# library('limma')
# library('tidyverse')
# library('DT')
# library('purrr')
# library('plotly')
# library('DESeq2')
# library("ggraph")
# library("igraph")
# source("utils.R")
```

```{r}
setwd(params$tempdir)
genesUp <- readRDS( "tmpResources/genesUp.Rds")
genesDown <- readRDS("tmpResources/genesDown.Rds")
kggUp <- readRDS( "tmpResources/kggUp.Rds")
kggDTup <- readRDS( "tmpResources/kggDTup.Rds")
goUp <- readRDS( "tmpResources/goUp.Rds")
goDTup <- readRDS( "tmpResources/goDTup.Rds")
kggDown <- readRDS( "tmpResources/kggDown.Rds")
kggDTdown <- readRDS( "tmpResources/kggDTdown.Rds")
goDown <- readRDS( "tmpResources/goDown.Rds")
goDTdown <- readRDS( "tmpResources/goDTdown.Rds")
dds <- readRDS("tmpResources/dds.Rds")
gsea <- readRDS("tmpResources/gsea.Rds")
```



Data preview
=====================================

Row
--------------------------------------

### Generic tab text

```{r results="asis", eval=TRUE}
texto <- "#### esto es un texto genérico que describe esta pestaña
aqui se pone cualquier cosa.

como si fuese un texto normal"
cat(texto)
```

Row
--------------------------------------

### Especific comment to results {data-width=500}

```{r results="asis"}

```


### Metata experiment {data-width=500}

```{r}

metadata <- as.data.frame(colData(dds))
metadata$sizeFactor <- round(metadata$sizeFactor,4)
datatable( metadata, 
           rownames=FALSE,
           filter = list(position="top", clear=FALSE),
           options = list(
               columnDefs = list(list(orderable = FALSE,
               className = "details-control",
               targets = 1),
               list(className = "dt-right", targets = 1:(ncol(metadata)-1))),
               dom = "Bfrtipl",
               buttons = c("copy", "csv", "excel", "pdf", "print"),
               list(pageLength = 10, white_space = "normal")))
```

Row
--------------------------------------

### DEseq results {data-width=500}

```{r}

```


### PCA gene expresión {data-width=500}

```{r}
plotPCA(rlog(dds), intgroup = params$variablepca )+
            theme(plot.margin=unit(c(0.5,0.5,0.5,0.5),"cm"))+
            theme(text = element_text(size=12))
```


All together {data-navmenu="Kegg"}
=====================================

Row
------------------------------------

### text 

```{r}

```


Row 
------------------------------------

### tabla {data-width=500}

```{r echo=FALSE}
predata <- kegg2DT(kggUp[params$nr, ], genesUp, nrows = length(params$nr))
datatable2( predata,
            vars = c("genes"),
            escape = FALSE,
            opts = list(pageLength = 10, white_space = "normal"))
```


### text1 {data-width=500}

```{r}

```

Row 
------------------------------------

### Lorem ipsum {data-width=500}

Lorem ipsum is simply dummy text of the printing and typesetting industry.
Lorem Ipsum has been the industry's standard dummy text ever since the 1500s,
when an unknown printer took a galley of type and scrambled it to make a type
specimen book. It has survived not only five centuries, but also the leap into
electronic typesetting, remaining essentially unchanged. It was popularised in
the 1960s with the release of Letraset sheets containing Lorem Ipsum passages,
and more recently with desktop publishing software like Aldus PageMaker
including versions of Lorem Ipsum.

* asñlfk
* sdfs
* sdfds

### text2 {data-width=500}

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.


Row
------------------------------------

### Barplot

```{r  echo=FALSE}
plotKegg(enrichdf = kggUp[params$nr,], nrows = length(params$nr) ) 
```

### ChorPlot

```{r echo=FALSE, warning=FALSE}
chordPlot(kggUp[params$nr, ], nRows = length(params$nr), orderby = "P.DE")
```

Row
------------------------------------

### Dotplot

```{r}
dotPlotkegg(kggUp[params$nr,], n = length(params$nr))+
        theme(text = element_text(size=10))
```


### Kegg heatmap

```{r}
heatmapKegg(kggDTup, params$nr)
```

Row
------------------------------------

### Kegg cnetplot

```{r}
customCnetKegg(kggUp, params$nr)
```

### 

```{r}

```


Upregulated {data-navmenu="Kegg"}
=====================================  

Row
------------------------------------

### text 

```{r}

```


Row 
------------------------------------

### tabla {data-width=500}

```{r echo=FALSE}
predata <- kegg2DT(kggUp[params$nr, ], genesUp, nrows = length(params$nr))
datatable2( predata,
            vars = c("genes"),
            escape = FALSE,
            opts = list(pageLength = 10, white_space = "normal"))
```


### text1 {data-width=500}

```{r}

```

Row 
------------------------------------

### Lorem ipsum {data-width=500}

Lorem ipsum is simply dummy text of the printing and typesetting industry.
Lorem Ipsum has been the industry's standard dummy text ever since the 1500s,
when an unknown printer took a galley of type and scrambled it to make a type
specimen book. It has survived not only five centuries, but also the leap into
electronic typesetting, remaining essentially unchanged. It was popularised in
the 1960s with the release of Letraset sheets containing Lorem Ipsum passages,
and more recently with desktop publishing software like Aldus PageMaker
including versions of Lorem Ipsum.

* asñlfk
* sdfs
* sdfds

### text2 {data-width=500}

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.


Row
------------------------------------

### Barplot

```{r  echo=FALSE}
plotKegg(enrichdf = kggUp[params$nr,], nrows = length(params$nr) ) 
```

### ChorPlot

```{r echo=FALSE, warning=FALSE}
chordPlot(kggUp[params$nr, ], nRows = length(params$nr), orderby = "P.DE")
```

Row
------------------------------------

### Dotplot

```{r}
dotPlotkegg(kggUp[params$nr,], n = length(params$nr))+
        theme(text = element_text(size=10))
```


### Kegg heatmap

```{r}
heatmapKegg(kggDTup, params$nr)
```

Row
------------------------------------

### Kegg cnetplot

```{r}
customCnetKegg(kggUp, params$nr)
```

### 

```{r}

```


Downregulated {data-navmenu="Kegg"}
=====================================

Row
------------------------------------

### text 

```{r}

```


Row 
------------------------------------

### tabla {data-width=500}

```{r echo=FALSE}
predata <- kegg2DT(kggUp[params$nr, ], genesUp, nrows = length(params$nr))
datatable2( predata,
            vars = c("genes"),
            escape = FALSE,
            opts = list(pageLength = 10, white_space = "normal"))
```


### text1 {data-width=500}

```{r}

```

Row 
------------------------------------

### Lorem ipsum {data-width=500}

Lorem ipsum is simply dummy text of the printing and typesetting industry.
Lorem Ipsum has been the industry's standard dummy text ever since the 1500s,
when an unknown printer took a galley of type and scrambled it to make a type
specimen book. It has survived not only five centuries, but also the leap into
electronic typesetting, remaining essentially unchanged. It was popularised in
the 1960s with the release of Letraset sheets containing Lorem Ipsum passages,
and more recently with desktop publishing software like Aldus PageMaker
including versions of Lorem Ipsum.

* asñlfk
* sdfs
* sdfds

### text2 {data-width=500}

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.


Row
------------------------------------

### Barplot

```{r  echo=FALSE}
plotKegg(enrichdf = kggUp[params$nr,], nrows = length(params$nr) ) 
```

### ChorPlot

```{r echo=FALSE, warning=FALSE}
chordPlot(kggUp[params$nr, ], nRows = length(params$nr), orderby = "P.DE")
```

Row
------------------------------------

### Dotplot

```{r}
dotPlotkegg(kggUp[params$nr,], n = length(params$nr))+
        theme(text = element_text(size=10))
```


### Kegg heatmap

```{r}
heatmapKegg(kggDTup, params$nr)
```

Row
------------------------------------

### Kegg cnetplot

```{r}
customCnetKegg(kggUp, params$nr)
```

### 

```{r}

```


All together {data-navmenu="GO BP"}
=====================================

Row
------------------------------------

### text 

```{r}

```


Row 
------------------------------------

### tabla {data-width=500}

```{r echo=FALSE}
predata <- kegg2DT(kggUp[params$nr, ], genesUp, nrows = length(params$nr))
datatable2( predata,
            vars = c("genes"),
            escape = FALSE,
            opts = list(pageLength = 10, white_space = "normal"))
```


### text1 {data-width=500}

```{r}

```

Row 
------------------------------------

### Lorem ipsum {data-width=500}

Lorem ipsum is simply dummy text of the printing and typesetting industry.
Lorem Ipsum has been the industry's standard dummy text ever since the 1500s,
when an unknown printer took a galley of type and scrambled it to make a type
specimen book. It has survived not only five centuries, but also the leap into
electronic typesetting, remaining essentially unchanged. It was popularised in
the 1960s with the release of Letraset sheets containing Lorem Ipsum passages,
and more recently with desktop publishing software like Aldus PageMaker
including versions of Lorem Ipsum.

* asñlfk
* sdfs
* sdfds

### text2 {data-width=500}

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.


Row
------------------------------------

### Barplot {data-width=500}

```{r  echo=FALSE}
plotKegg(enrichdf = kggUp[params$nr,], nrows = length(params$nr) ) 
```

### ChorPlot {data-width=500}

```{r echo=FALSE, warning=FALSE}
chordPlot(kggUp[params$nr, ], nRows = length(params$nr), orderby = "P.DE")
```

Row
------------------------------------

### Dotplot {data-width=500}

```{r}
dotPlotkegg(kggUp[params$nr,], n = length(params$nr))+
        theme(text = element_text(size=10))
```


### Kegg heatmap {data-width=500}

```{r}
heatmapKegg(kggDTup, params$nr)
```

Row
------------------------------------

### Kegg cnetplot {data-width=500}

```{r}
customCnetKegg(kggUp, params$nr)
```

### {data-width=500}

```{r}

```

Upregulated {data-navmenu="GO BP"}
=====================================

Downregulated {data-navmenu="GO BP"}
=====================================

All together {data-navmenu="GO MF"}
=====================================

Upregulated {data-navmenu="GO MF"}
=====================================

Downregulated {data-navmenu="GO MF"}
=====================================

All together {data-navmenu="GO CC"}
=====================================

Upregulated {data-navmenu="GO CC"}
=====================================

Downregulated {data-navmenu="GO CC"}
=====================================

GSEA
=====================================

Row
-------------------------------------

### Generic and specific text

```{r}

```

Row
------------------------------------

### Table GSEA {data-width=500}

```{r}

```

### Plot GSEA {data-width=500}

```{r}

```

