---
title: "RNAseq viewer report"
author: "Miriam RIQUELME"
date: 2020
output:
  rmdformats::readthedown:
    highlight: kate
params:
  nr: NA
  bpnr: NA
  ccnr: NA
  mfnr: NA
  nrdown: NA
  bpnrdown: NA
  mfnrdown: NA
  ccnrdown: NA
  variablepca: NA
  tempdir: NA
  gseanr: NA
---


```{r results="asis", echo=FALSE}
cat("
<style>
#content {
  max-width: 1080px;
  margin-left: 300px;
  background: #edf0f2;
}
</style>
")
```

```{r setup, echo=FALSE, include=FALSE, comment=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.width = 12)
setwd(params$tempdir)
library(shinydashboard)
library(limma)
library(tidyverse)
library(DT)
library(purrr)
library(plotly)
library(DESeq2)
source("utils.R")
genesUp <- readRDS( "genesUp.Rds")
genesDown <- readRDS("genesDown.Rds")
kggUp <- readRDS( "kggUp.Rds")
kggDTup <- readRDS( "kggDTup.Rds")
goUp <- readRDS( "goUp.Rds")
goDTup <- readRDS( "goDTup.Rds")
kggDown <- readRDS( "kggDown.Rds")
kggDTdown <- readRDS( "kggDTdown.Rds")
goDown <- readRDS( "goDown.Rds")
goDTdown <- readRDS( "goDTdown.Rds")
dds <- readRDS("deseq.Rds")
gsea <- readRDS("gsea.Rds")
```

# Data preview

## Metata experiment

```{r}
metadata <- as.data.frame(colData(dds))
metadata$sizeFactor <- round(metadata$sizeFactor,4)
datatable( metadata, filter = list(position="top", clear=FALSE),
           options = list(
               columnDefs = list(list(orderable = FALSE,
               className = "details-control",
               targets = 1),
               list(className = "dt-right", targets = 1:ncol(metadata))),
               dom = "Bfrtipl",
               buttons = c("copy", "csv", "excel", "pdf", "print"),
               list(pageLength = 10, white_space = "normal")))
```

## PCA gene expresión

```{r}
plotPCA(rlog(dds), intgroup = params$variablepca )+
            theme(plot.margin=unit(c(0.5,0.5,0.5,0.5),"cm"))+
            theme(text = element_text(size=12))
```

## Gene Expression results

```{r}
res <- results(dds)
res <- as.data.frame(res)
datatable(
    round(res, 4),
    filter = list(position = "top", clear = FALSE),
    options = list(
        columnDefs = list(
            list(
                orderable = FALSE,
                className = "details-control",
                targets = 1
            ),
            list(className = "dt-right", targets = 1:ncol(res))
        ),
        dom = "Bfrtipl",
        buttons = c("copy", "csv", "excel", "pdf", "print"),
        list(pageLength = 10, white_space = "normal")
    )
)
```

# Kegg pathways enrichment

## Kegg enrichment Upregulated

```{r echo=FALSE}
predata <- kegg2DT(kggUp[params$nr, ], genesUp, nrows = length(params$nr))
datatable2( predata,
            vars = c("genes"),
            escape = FALSE,
            opts = list(pageLength = 10, white_space = "normal"))
```

### Kegg barplot

```{r  echo=FALSE}
plotKegg(enrichdf = kggUp[params$nr,], nrows = length(params$nr) ) 
```

### Kegg chordplot

```{r echo=FALSE, warning=FALSE}
chordPlot(kggUp[params$nr, ], nRows = length(params$nr), orderby = "P.DE")
```

### Kegg dotplot

```{r}
dotPlotkegg(kggUp[params$nr,], n = length(params$nr))+
        theme(text = element_text(size=10))
```

### Kegg heatmap

```{r}
heatmapKegg(kggDTup, params$nr)
```

### Kegg cnetplot

```{r}
customCnetKegg(kggUp, params$nr)
```


## Kegg enrichment Downregulated

```{r echo=FALSE}
predata <- kegg2DT(kggDown[params$nrdown, ], genesDown, nrows = length(params$nrdown))
datatable2( predata,
            vars = c("genes"),
            escape = FALSE,
            opts = list(pageLength = 10, white_space = "normal"))
```

### Kegg barplot

```{r  echo=FALSE}
plotKegg(enrichdf = kggDown[params$nrdown,], nrows = length(params$nrdown) ) 
```

### Kegg chordplot

```{r echo=FALSE, warning=FALSE}
chordPlot(kggDown[params$nrdown, ], nRows = length(params$nrdown), orderby = "P.DE")
```

### Kegg dotplot

```{r}
dotPlotkegg(kggDown[params$nrdown,], n = length(params$nrdown))+
        theme(text = element_text(size=10))
```

### Kegg heatmap

```{r}
heatmapKegg(kggDTdown, params$nrdown)
```

### Kegg cnetplot

```{r}
customCnetKegg(kggDown, params$nrdown)
```

# Gene Ontology enrichment

## GO Biological Proccess Upregulated

```{r echo=FALSE, eval=TRUE}
gosbp <- goUp[goUp$Ont=="BP",]
goDT <- go2DT(enrichdf = gosbp[params$bpnr, ], data = genesUp, nrows = length(params$bpnr))
datatable2(goDT, vars = c("genes"),
           escape = FALSE,
           opts = list(pageLength = 10, white_space = "normal"))
```

### BP barplot 

```{r echo=FALSE, eval=TRUE}
plotGO(enrichdf = gosbp[params$bpnr,], nrows = length(params$bpnr), ont="BP")
```

### BP dotplot

```{r}
dotPlotGO(gosbp[params$bpnr,], n = length(params$bpnr))+
        theme(text = element_text(size=10))
```

## GO Molecular Function Upregulated

```{r echo=FALSE, eval=TRUE}
gosbp <- goUp[goUp$Ont=="MF",]
goDT <- go2DT(enrichdf = gosbp[params$mfnr, ], data = genesUp, nrows = length(params$mfnr))
datatable2(goDT, vars = c("genes"),
           escape = FALSE,
           opts = list(pageLength = 10, white_space = "normal"))
```

### MF barplot

```{r echo=FALSE, eval=TRUE}
plotGO(enrichdf = gosbp[params$mfnr,], nrows = length(params$mfnr), ont="MF")
```

### MF dotplot

```{r}
dotPlotGO(gosbp[params$mfnr,], n = length(params$mfnr))+
        theme(text = element_text(size=10))
```

## GO Cellular Component Upregulated

```{r echo=FALSE, eval=TRUE}
gosbp <- goUp[goUp$Ont=="CC",]
goDT <- go2DT(enrichdf = gosbp[params$ccnr, ], data = genesUp, nrows = length(params$ccnr))
datatable2(goDT, vars = c("genes"),
           escape = FALSE,
           opts = list(pageLength = 10, white_space = "normal"))
```

### CC barplot

```{r echo=FALSE, eval=TRUE}
plotGO(enrichdf = gosbp[params$ccnr,], nrows = length(params$ccnr), ont="CC")
```

### CC dotplot

```{r}
dotPlotGO(gosbp[params$ccnr,], n = length(params$ccnr))+
        theme(text = element_text(size=10))
```


## GO Biological Proccess Downregulated

```{r echo=FALSE, eval=TRUE}
gosbp <- goDown[goDown$Ont=="BP",]
goDT <- go2DT(enrichdf = gosbp[params$bpnrdown, ],
              data = genesDown, nrows = length(params$bpnrdown))
datatable2(goDT, vars = c("genes"),
           escape = FALSE,
           opts = list(pageLength = 10, white_space = "normal"))
```

### BP barplot 

```{r echo=FALSE, eval=TRUE}
plotGO(enrichdf = gosbp[params$bpnrdown,], nrows = length(params$bpnrdown), ont="BP")
```

### BP dotplot

```{r}
dotPlotGO(gosbp[params$bpnrdown,], n = length(params$bpnrdown))+
        theme(text = element_text(size=10))
```

## GO Molecular Function Upregulated

```{r echo=FALSE, eval=TRUE}
gosbp <- goDown[goDown$Ont=="MF",]
goDT <- go2DT(enrichdf = gosbp[params$mfnrdown, ],
              data = genesDown, nrows = length(params$mfnrdown))
datatable2(goDT, vars = c("genes"),
           escape = FALSE,
           opts = list(pageLength = 10, white_space = "normal"))
```

### MF barplot

```{r echo=FALSE, eval=TRUE}
plotGO(enrichdf = gosbp[params$mfnrdown,], nrows = length(params$mfnrdown), ont="MF")
```

### MF dotplot

```{r}
dotPlotGO(gosbp[params$mfnrdown,], n = length(params$mfnrdown))+
        theme(text = element_text(size=10))
```

## GO Cellular Component Upregulated

```{r echo=FALSE, eval=TRUE}
gosbp <- goDown[goDown$Ont=="CC",]
goDT <- go2DT(enrichdf = gosbp[params$ccnrdown, ],
              data = genesDown, nrows = length(params$ccnrdown))
datatable2(goDT, vars = c("genes"),
           escape = FALSE,
           opts = list(pageLength = 10, white_space = "normal"))
```

### CC barplot

```{r echo=FALSE, eval=TRUE}
plotGO(enrichdf = gosbp[params$ccnrdown,], nrows = length(params$ccnrdown), ont="CC")
```

### CC dotplot

```{r}
dotPlotGO(gosbp[params$ccnrdown,], n = length(params$ccnrdown))+
        theme(text = element_text(size=10))
```

# Gene Set Enrichment Analysis

## GSEA results

```{r}
table <- gsea@result[gsea@result$p.adjust <= 0.05 , 2:9] %>%
  mutate_at(vars(3:7), ~ round(., 3))
DT::datatable(
  table,
  rownames = FALSE,
  filter = list(position = "top", clear = FALSE),
  options = list(
    columnDefs = list(
      list(
        orderable = FALSE,
        className = "details-control",
        targets = 1
      )
    ),
    dom = "Bfrtipl",
    buttons = c("copy", "csv", "excel", "pdf", "print"),
    list(pageLength = 10, white_space = "normal")
  )
)
```

## GSEA plot

```{r fig.width=12}
enrichplot::gseaplot2(gsea, geneSetID = params$gseanr, pvalue_table = TRUE, ES_geom = "line")
```

